---
title: "upwaver"
author: "Adrian Stämpfli and Michael Schmid, IMS-FHS"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{upwaver}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE, message=FALSE, results='hide'}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
# knitr::opts_chunk$set(results = 'hide')
```

<!-- Code for adding footnotes: footnotes^[This is a footnote.] -->

'upwaver' is a wrapper around the 'Upwave' API that allows users to access the 'Upwave' API from 
within R.  
  
While using 'Upwave' (https://www.upwave.io/) you might come to a point where you want to 
extract detailed information of ongoing projects or you might want to upload Cards to certain
Boards directly out of a Excel sheet. 'upwaver' is a small tool to solve such problems without 
copy-pasting a lot of content.  

The package was designed based on the given 'Upwave' API (https://upwavehq.github.io/api/).


## Basics about 'Upwave' and 'upwaver'

#### Your Domain
Each organisation (company, team) with an 'Upwave' account has its own `<TEAM_DOMAIN>`. 
You can see this on the frontpage of your 'Upwave' account: (`https://<TEAM_DOMAIN>.upwave.io`). 
The 'upwaver' package refers to this `<TEAM_DOMAIN>` as `organisation`.  
  
#### Authentication
To access information of your account (domain), you need an access token. It can be obtained 
by visiting your account settings. Click your profile image, select “Settings” and find your 
API-Key in the “Account” tab. The 'upwaver' package refers to the API-Key as `token`. 
  
#### Boards
An 'Upwave' account consits of different Boards (projects) on which an organisation works
simultaneously. The 'upwaver' package identifies a Board with the `board_id` and `board_name`. 

 * `board_name`: it's the casual name (title) you give to a Board 
 * `board_id`: That's the unique ID you see in the browser-link when watching your Board (i.e: 
    `https://<TEAM_DOMAIN>.upwave.io/board/board_id/view/...`)

#### Cards
Each Board consits of different Cards which can be seen as lots of "work packages". The contain
Information about the actual tasts to do inside the project. They are the objects to talk 
to when using 'upwaver' 


## Getting Board- & Card- information from 'Upwave'
The 'upwaver' package gives three basic functionalities to directly access 'Upwave' information. 

 * [List of Boards](#list_of_boards) 
 * [Board details](#board_details)
 * [List of Cards](#list_of_cards)


#### List of Boards {#list_of_boards}
Use `list_boards()` to get a list of all boards of your organisation. Archived boards will
not be shown in this list.
```{r}
my_board_list <- upwaver::list_boards("ims-fhs", "a44fa67c5df2acc9836058ffca870d7b78b017cb")
my_board_list$count
summary(my_board_list)
summary(my_board_list$results[[1]])
```


#### Board details {#board_details}
Use `board_details()` to get detailed background Information about a specific board. 
```{r}
my_board_details <- upwaver::board_details("ims-fhs", 14351, "a44fa67c5df2acc9836058ffca870d7b78b017cb")
summary(my_board_details)
```


#### List of Cards {#list_of_cards}
Use `list_cards()` to get detailed Information about all Cards of a specific board. This 
includes cards that are marked as completed. 
```{r}
my_card_list <- upwaver::list_cards("ims-fhs", 14351, "a44fa67c5df2acc9836058ffca870d7b78b017cb")
my_card_list$count
summary(my_card_list)
summary(my_card_list$results[[1]])
```


## Getting Storypoints-Information from 'Upwave'
An additional feature of upwaver is the `storypoints_and_status()` function. It's was designed by our 
institue for internal reasons. Nevertheless it might be useful for your organisation as well.  
  
If working with agile methods (i.e. SCRUM, agile testing, ASD, ...) you might want to work with
storypoints in order to estimate time resources. Our institute works with storypoints in the 
following way. Each 'Upwave' Card has a short text at the bottom the Card description that says:  
**"Aufwand: X SP"** or **"Aufwand: X AT"** as an indicator for the estimated storypoints. 
The value `X`, title and status of every Card is be caught by `storypoints_and_status()` and
given as a list. 
```{r}
my_storypoints <- upwaver::storypoints_and_status("ims-fhs", 14351, "a44fa67c5df2acc9836058ffca870d7b78b017cb")
my_storypoints$storypoints_status
my_storypoints$sum_storypoints
```


## Create a Userstory (Card) on 'Upwave'
For own puposes we created a function that directly uploads Userstorys to the leftmost column of
a desired Board from a local excel file. This might me helfpul when a list of basic tasks has
been defined in an exel-sheet during a meeting or similar and you don't want to copy paste it 
all into 'Upwave' 

The function needs several input parameters to coordinate the source (excel file) with the 
desired 'Upwave' Board. Keep in mind that the excel file needs the following three columns: 

  * `US-ID`: The Number you want to give to your Card (Userstory)
  * `name`: The name (title) of your Userstory
  * `description`: The description of your Userstory
  
```{r}
# create_card_from_excel(
#   excel_file = "path_to_your_excel_file", 
#   sheet = "name_of_the_excel_sheet" or number_of_the_excel_sheet, 
#   line_number = line_nr_you_want_to_upload, 
#   organisation = "your_organisation", 
#   board_id = your_board_id, 
#   board_name = "your_board_name", 
#   token = "your_token")
```

To upload several Cards, we recomment a simple for-loop
```{r}
# for (i in 1:30) {
#   create_card_from_excel(..., line_number = i, ...)
# }
```


